When are Fuzzy Extractors Possible?

### 2014-11-24 info-bounds/FuzzyExtPossibility.tex
added acks

\title{When are Fuzzy Extractors Possible?}
\blind{
\author{
Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.  Boston University and MIT Lincoln Laboratory. The Lincoln Laboratory portion of this work was sponsored by the Department of the Air Force under Air Force Contract \#FA8721-05-C-0002.  Opinions, interpretations, conclusions and recommendations are those of the author and are not necessarily endorsed by the United States Government.}  \and Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.  Boston University.} \and Adam Smith\footnote{Email: {\tt asmith@cse.psu.edu}.  Pennsylvania State University; work performed while at Boston University's Hariri Institute for Computing and RISCS Center, and Harvard University's
``Privacy Tools'' project.}}
}
\begin{document}
\maketitle

@@

\paragraph{Comparison with \thref{thm:imposs sketch}} The parameters in this result are weaker than those in \thref{thm:imposs sketch}.  This result requires: 1) higher error tolerance $t= \omega(n^{1/2}\log n)$ 2) the fuzzy extractor must have perfect correctness.  The secure sketch counter example needs $t=4$ and allows the $\rec$ to be wrong almost $1/4$ of the time.
\bibliographystyle{alpha}
\bibliography{crypto}

>>>>

\title{When are Fuzzy Extractors Possible?}
\blind{
\author{
Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.  Boston University and MIT Lincoln Laboratory.}  \and Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.  Boston University.} \and Adam Smith\footnote{Email: {\tt asmith@cse.psu.edu}.  Pennsylvania State University; work performed while at Boston University's Hariri Institute for Computing and RISCS Center, and Harvard University's
``Privacy Tools'' project.}}
}
\begin{document}
\maketitle

@@

\paragraph{Comparison with \thref{thm:imposs sketch}} The parameters in this result are weaker than those in \thref{thm:imposs sketch}.  This result requires: 1) higher error tolerance $t= \omega(n^{1/2}\log n)$ 2) the fuzzy extractor must have perfect correctness.  The secure sketch counter example needs $t=4$ and allows the $\rec$ to be wrong almost $1/4$ of the time.

\section*{Acknowledgements}
The authors are grateful to Gene Itkis and Yevgeniy Dodis for helpful discussions.
The work of Benjamin Fuller is sponsored in part by US NSF grants 1012910 and 1012798 and  the United States Air Force under Air Force Contract FA8721-05-C-0002. Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government. 
Leonid Reyzin is supported in part by US NSF grants 0831281, 1012910, 1012798, and 1422965.

\bibliographystyle{alpha}
\bibliography{crypto}
